Algomusicology, ????, Profit

### 2016-04-03 paper.tex
Add understated irony.

Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a field,
so they advised DJs to "have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
music in the event of police harassment."\cite{Joseph Gallivan on pop}

>>>>

Autechre appreciated the practical difficulties of negotiating the subtleties of complexity theory at 3am in a noisy field,
so they advised DJs to "have a lawyer and a musicologist present at all times to confirm the non repetitive nature of the
music in the event of police harassment."\cite{Joseph Gallivan on pop}
